### 2021-01-22 paper1/paper1.tex
Some meager progress

\subsection{Data}
We run experiments on two real-world datasets.
The first dataset is the \textbf{Adult Income} dataset~\citep{Dua:2017}.
It contains 33,561 data points with census information from US citizens.
The labels indicate whether the individual earns more ($y=1$) or less ($y=0$) than \$50,000 per year.
We use the dataset with either \emph{race} or \emph{gender} as the sensitive attribute.
The input dimension, excluding the sensitive attributes, is 12 in the raw data;
the categorical features are then one-hot encoded.
For the experiments, we removed 2,399 instances with missing data
and used only the training data, which we split randomly for each trial run.
%
The second dataset is the \textbf{ProPublica recidivism} dataset.
It contains data from 6,167 individuals that were arrested.
The data was collected when investigating the COMPAS risk assessment tool~\citep{angwin2016machine}.
The task is to predict whether the person was rearrested within two years
($y=1$ if they were rearrested, $y=0$ otherwise).
We again use the dataset with either \emph{race} or \emph{gender} as the sensitive attributes.

@@

\subsection{Method}
\begin{table*}[tb]
\caption{%
  Accuracy and fairness (with respect to \emph{demographic parity}) for various methods
  on the balanced test set of the Adult dataset.
  Fairness is defined as $\textit{PR}_{s=0}/\textit{PR}_{s=1}$ (a completely fair model would achieve a value of 1.0).
  Left: using \textbf{race} as the sensitive attribute. Right: using \textbf{gender} as the sensitive attribute.
  The mean and std of $10$ repeated experiments.
}%
\label{tab:dempar}%\scalebox{0.99}{%
\centering
\resizebox{\textwidth}{!}{
  \begin{tabular}{l@{\hskip 0.25cm}l@{\hskip 0.25cm}l}
    \toprule
  Algorithm &   Fair $\rightarrow 1.0 \leftarrow$&           Accuracy $\uparrow$\\
  % Algorithm &   Fairness &           Accuracy \\
    \midrule
                   GP &  0.80 $\pm$ 0.07 &  0.888 $\pm$ 0.007 \\
               LR &  0.83 $\pm$ 0.06 &  0.884 $\pm$ 0.007 \\
              SVM &  0.89 $\pm$ 0.06 &  0.899 $\pm$ 0.004 \\
           FairGP (ours) &  0.86 $\pm$ 0.07 &  0.888 $\pm$ 0.006 \\
           FairLR (ours) &  0.90 $\pm$ 0.06 &  0.874 $\pm$ 0.009 \\
    ZafarAccuracy &  0.67 $\pm$ 0.17 &  0.808 $\pm$ 0.016 \\
    ZafarFairness &  0.81 $\pm$ 0.06 &  0.879 $\pm$ 0.009 \\
    \citet{kamiran2012data} &  0.87 $\pm$ 0.07 &  0.882 $\pm$ 0.007 \\
    \citet{AgaBeyDudLanetal18} & 0.86 $\pm$ 0.08 & 0.883 $\pm$ 0.008 \\
    \bottomrule
  \end{tabular}%}
  % \hspace{0.25cm}
  \;
  %\scalebox{0.99}{%
  \begin{tabular}{l@{\hskip 0.25cm}l}
    \toprule
    Fair $\rightarrow 1.0 \leftarrow$ &           Accuracy $\uparrow$\\
  % Algorithm &   Fairness &           Accuracy \\
    \midrule
       0.54 $\pm$ 0.05 &  0.900 $\pm$ 0.006 \\
       0.52 $\pm$ 0.03 &  0.898 $\pm$ 0.003 \\
       0.49 $\pm$ 0.05 &  0.913 $\pm$ 0.004 \\
       0.87 $\pm$ 0.09 &  0.902 $\pm$ 0.007 \\
       0.93 $\pm$ 0.04 &  0.886 $\pm$ 0.012 \\
       0.77 $\pm$ 0.08 &  0.853 $\pm$ 0.017 \\
       0.74 $\pm$ 0.11 &  0.897 $\pm$ 0.004 \\
       0.96 $\pm$ 0.03 &  0.900 $\pm$ 0.004 \\
       0.65 $\pm$ 0.04 &  0.900 $\pm$ 0.004 \\
    \bottomrule
  \end{tabular}%}
}
\end{table*}%
We evaluate two versions of our target label model\footnote{%
The code %is available in the supplementary folder.
can be found on GitHub: \url{https://github.com/predictive-analytics-lab/ethicml-models/tree/master/implementations/fairgp}.
}:
% \url{https://github.com/predictive-analytics-lab/UniversalGP}.}:
\emph{FairGP}, which is based on Gaussian Process models, and \emph{FairLR}, which is based on logistic regression.
We also train baseline models that do not take fairness into account.

@@

\subsection{Results for Demographic Parity on Adult dataset}\label{sssec:demparresults}
% \noindent\textbf{Results for Demographic Parity on Adult dataset.}
\begin{figure}[t]
  \begin{center}
    \centerline{\includegraphics[width=0.98\columnwidth]{./figures/adult_tar_choice.eps}}
    \caption{Accuracy and fairness (demographic parity) for various target choices.
      (a): Adult dataset using race as the sensitive attribute;
      (b): Adult dataset using gender.
      Centre of the cross is the mean; height and width of the box encode half of standard derivation of accuracy and disparate impact.
    }%
    \label{fig:tar}
  \end{center}
  % \vspace*{-0.8cm}
% \caption{Accuracy and fairness for various targets.  w.r.t. accuracy and width of the box encodes standard derivation w.r.t. fairness criterion}
\end{figure}%
%
Following \citet{zafar2017fairnessconstraints} we evaluate demographic parity on the Adult dataset.
Table~\ref{tab:dempar} shows the accuracy and fairness for several algorithms.
In the table, and in the following, we use $\mathit{PR}_{s=i}$ to denote
the observed rate of positive predictions per demographic group $P (\hat{y} = 1 | s =i)$.
Thus, $\mathit{PR}_{s=0} / \mathit{PR}_{s=1}$ is a measure for demographic parity,
where a completely fair model would attain a value of $1.0$.
This measure for demographic parity is also called ``disparate impact''
(see e.g.~\citet{feldman2015certifying,zafar2017fairnesstreatment}).
%
As the results in Table~\ref{tab:dempar} show, FairGP and FairLR are clearly fairer than the baseline GP and LR\@.
We use the mean ($\mathit{PR}_t^{avg}$) for the target acceptance rate.
The difference between fair models and unconstrained models is not as large with \emph{race} as the sensitive attribute,
as the unconstrained models are already quite fair there.
The results of FairGP are characterised by high fairness and high accuracy.
FairLR achieves similar results to FairGP, but with generally slightly lower accuracy but better fairness.
We used the two step procedure of \citet{DonOneBenShaetal18}
to verify that we cannot achieve the same fairness result with just parameter search on LR\@.

@@

\subsection{Results for Equality of Opportunity on ProPublica dataset.}\label{sssec:eqoppresults}
% \noindent\textbf{Results for Equality of Opportunity on ProPublica dataset.}
%
For equality of opportunity,
we again follow \citet{zafar2017fairnesstreatment} and evaluate the algorithm on the ProPublica dataset.
As we did for demographic parity,
we define a measure of equality of opportunity via the ratio of the true positive rates (TPRs) within the demographic groups.
We use $\mathit{TPR}_{s=i}$ to denote the observed TPR in group $i$: $P(\hat{y}=1|y=1, s=i)$,
and $\mathit{TNR}_{s=i}$ for the observed true negative rate (TNR) in the same manner.
The measure is then given by $\mathit{TPR}_{s=0} / \mathit{TPR}_{s=1}$.
A perfectly fair algorithm would achieve $1.0$ on the measure.
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_box_with_agarwal.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_race_opp_box.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_sex_opp_box.eps}
  \caption{Accuracy and fairness (with respect to \emph{equality of opportunity}) for various methods on ProPublica dataset.
    \textbf{(a)}: using race as the sensitive attribute; \textbf{(b)}: using gender.
    A completely fair model would achieve a value of 1.0 in the x-axis.
    %The best value for the TPR ratio is $1.0$.
    See Fig.~\ref{fig:propublica_opp_scatter_tpr}(a) and (b) on how these choices of PR setting translate to
    $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$. %and TPR vs TNR.
  }%
  \label{fig:propublica_opp_box}
\end{figure*}
\begin{figure*}[!ht]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_scatter_tpr.eps}
  \caption{%
    Fairness measure $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$ (\emph{equality of opportunity}) for different target PRs ($\mathit{PR}_t$).
    (a): on dataset ProPublica recidivism using race as the sensitive attribute;
    (b): using gender.
  }%
  \label{fig:propublica_opp_scatter_tpr}
\end{figure*}

@@

We refer to the set $\mathcal{A} = (\mathcal{C}^0\cap\mathcal{Y}^0) \cup (\mathcal{C}^1\cap\mathcal{Y}^1)$
as the set of correct (or \textbf{a}ccurate) predictions.
The \emph{accuracy} is given by $\mathit{acc} = N^{-1}\cdot\left|\mathcal{A}\right|$.
From the definition it is clear that $0\leq\mathit{acc} \leq 1$.

>>>>

\subsection{Data}
We run experiments on two real-world datasets.
The first dataset is the \textsc{Adult Income} dataset~\citep{Dua:2017}.
It contains 33,561 data points with census information from US citizens.
The labels indicate whether the individual earns more ($y=1$) or less ($y=0$) than \$50,000 per year.
We use the dataset with either \emph{race} or \emph{gender} as the sensitive attribute.
The input dimension, excluding the sensitive attributes, is 12 in the raw data;
the categorical features are then one-hot encoded.
For the experiments, we removed 2,399 instances with missing data
and used only the training data, which we split randomly for each trial run.
%
The second dataset is the \textsc{ProPublica recidivism} dataset.
It contains data from 6,167 individuals that were arrested.
The data was collected when investigating the COMPAS risk assessment tool~\citep{angwin2016machine}.
The task is to predict whether the person was rearrested within two years
($y=1$ if they were rearrested, $y=0$ otherwise).
We again use the dataset with either \emph{race} or \emph{gender} as the sensitive attributes.

@@

\subsection{Method}
\begin{table*}[tb]
\caption{%
  Accuracy and fairness (with respect to \emph{demographic parity}) for various methods
  on the balanced test set of the Adult dataset.
  Fairness is defined as $\textit{PR}_{s=0}/\textit{PR}_{s=1}$ (a completely fair model would achieve a value of 1.0).
  Left: using \textsc{race} as the sensitive attribute. Right: using \textsc{gender} as the sensitive attribute.
  The mean and std of $10$ repeated experiments.
}%
\label{tab:dempar}%\scalebox{0.99}{%
\centering
\resizebox{\textwidth}{!}{
  \begin{tabular}{l@{\hskip 0.25cm}l@{\hskip 0.25cm}l}
    \toprule
  Algorithm &   Fair $\rightarrow 1.0 \leftarrow$&           Accuracy $\uparrow$\\
  % Algorithm &   Fairness &           Accuracy \\
    \midrule
                   GP &  0.80 $\pm$ 0.07 &  0.888 $\pm$ 0.007 \\
               LR &  0.83 $\pm$ 0.06 &  0.884 $\pm$ 0.007 \\
              SVM &  0.89 $\pm$ 0.06 &  0.899 $\pm$ 0.004 \\
           FairGP (ours) &  0.86 $\pm$ 0.07 &  0.888 $\pm$ 0.006 \\
           FairLR (ours) &  0.90 $\pm$ 0.06 &  0.874 $\pm$ 0.009 \\
    ZafarAccuracy &  0.67 $\pm$ 0.17 &  0.808 $\pm$ 0.016 \\
    ZafarFairness &  0.81 $\pm$ 0.06 &  0.879 $\pm$ 0.009 \\
    \citet{kamiran2012data} &  0.87 $\pm$ 0.07 &  0.882 $\pm$ 0.007 \\
    \citet{AgaBeyDudLanetal18} & 0.86 $\pm$ 0.08 & 0.883 $\pm$ 0.008 \\
    \bottomrule
  \end{tabular}%}
  % \hspace{0.25cm}
  \;
  %\scalebox{0.99}{%
  \begin{tabular}{l@{\hskip 0.25cm}l}
    \toprule
    Fair $\rightarrow 1.0 \leftarrow$ &           Accuracy $\uparrow$\\
  % Algorithm &   Fairness &           Accuracy \\
    \midrule
       0.54 $\pm$ 0.05 &  0.900 $\pm$ 0.006 \\
       0.52 $\pm$ 0.03 &  0.898 $\pm$ 0.003 \\
       0.49 $\pm$ 0.05 &  0.913 $\pm$ 0.004 \\
       0.87 $\pm$ 0.09 &  0.902 $\pm$ 0.007 \\
       0.93 $\pm$ 0.04 &  0.886 $\pm$ 0.012 \\
       0.77 $\pm$ 0.08 &  0.853 $\pm$ 0.017 \\
       0.74 $\pm$ 0.11 &  0.897 $\pm$ 0.004 \\
       0.96 $\pm$ 0.03 &  0.900 $\pm$ 0.004 \\
       0.65 $\pm$ 0.04 &  0.900 $\pm$ 0.004 \\
    \bottomrule
  \end{tabular}%}
}
\end{table*}%
We evaluate two versions of our target label model\footnote{%
The code %is available in the supplementary folder.
can be found on GitHub: \url{https://github.com/predictive-analytics-lab/ethicml-models/tree/master/implementations/fairgp}.
}:
% \url{https://github.com/predictive-analytics-lab/UniversalGP}.}:
\emph{FairGP}, which is based on Gaussian Process models, and \emph{FairLR}, which is based on logistic regression.
We also train baseline models that do not take fairness into account.

@@

\subsection{Results for Demographic Parity on Adult dataset}\label{sssec:demparresults}
\begin{figure}[t]
  \begin{center}
    \centerline{\includegraphics[width=0.98\columnwidth]{./figures/adult_tar_choice.eps}}
    \caption{Accuracy and fairness (demographic parity) for various target choices.
      (a): Adult dataset using race as the sensitive attribute;
      (b): Adult dataset using gender.
      Centre of the cross is the mean; height and width of the box encode half of standard derivation of accuracy and disparate impact.
    }%
    \label{fig:tar}
  \end{center}
  % \vspace*{-0.8cm}
% \caption{Accuracy and fairness for various targets.  w.r.t. accuracy and width of the box encodes standard derivation w.r.t. fairness criterion}
\end{figure}%
%
Following \citet{zafar2017fairnessconstraints} we evaluate demographic parity on the Adult dataset.
Table~\ref{tab:dempar} shows the accuracy and fairness for several algorithms.
In the table, and in the following, we use $\mathit{PR}_{s=i}$ to denote
the observed rate of positive predictions per demographic group $P (\hat{y} = 1 | s =i)$.
Thus, $\mathit{PR}_{s=0} / \mathit{PR}_{s=1}$ is a measure for demographic parity,
where a completely fair model would attain a value of $1.0$.
This measure for demographic parity is also called ``disparate impact''
(see e.g.~\citet{feldman2015certifying,zafar2017fairnesstreatment}).
%
As the results in Table~\ref{tab:dempar} show, FairGP and FairLR are clearly fairer than the baseline GP and LR\@.
We use the mean ($\mathit{PR}_t^{avg}$) for the target acceptance rate.
The difference between fair models and unconstrained models is not as large with \emph{race} as the sensitive attribute,
as the unconstrained models are already quite fair there.
The results of FairGP are characterised by high fairness and high accuracy.
FairLR achieves similar results to FairGP, but with generally slightly lower accuracy but better fairness.
We used the two step procedure of \citet{DonOneBenShaetal18}
to verify that we cannot achieve the same fairness result with just parameter search on LR\@.

@@

\subsection{Results for Equality of Opportunity on ProPublica dataset.}\label{sssec:eqoppresults}
%
For equality of opportunity,
we again follow \citet{zafar2017fairnesstreatment} and evaluate the algorithm on the ProPublica dataset.
As we did for demographic parity,
we define a measure of equality of opportunity via the ratio of the true positive rates (TPRs) within the demographic groups.
We use $\mathit{TPR}_{s=i}$ to denote the observed TPR in group $i$: $P(\hat{y}=1|y=1, s=i)$,
and $\mathit{TNR}_{s=i}$ for the observed true negative rate (TNR) in the same manner.
The measure is then given by $\mathit{TPR}_{s=0} / \mathit{TPR}_{s=1}$.
A perfectly fair algorithm would achieve $1.0$ on the measure.
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_box_with_agarwal.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_race_opp_box.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_sex_opp_box.eps}
  \caption{Accuracy and fairness (with respect to \emph{equality of opportunity}) for various methods on ProPublica dataset.
    (a): using race as the sensitive attribute; (b): using gender.
    A completely fair model would achieve a value of 1.0 in the x-axis.
    %The best value for the TPR ratio is $1.0$.
    See Fig.~\ref{fig:propublica_opp_scatter_tpr}(a) and (b) on how these choices of PR setting translate to
    $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$. %and TPR vs TNR.
  }%
  \label{fig:propublica_opp_box}
\end{figure*}
\begin{figure*}[!ht]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_scatter_tpr.eps}
  \caption{%
    Fairness measure $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$ (\emph{equality of opportunity}) for different target PRs ($\mathit{PR}_t$).
    (a): on dataset ProPublica recidivism using race as the sensitive attribute;
    (b): using gender.
  }%
  \label{fig:propublica_opp_scatter_tpr}
\end{figure*}

@@

We refer to the set $\mathcal{A} = (\mathcal{C}^0\cap\mathcal{Y}^0) \cup (\mathcal{C}^1\cap\mathcal{Y}^1)$
as the set of correct (or \emph{a}ccurate) predictions.
The \emph{accuracy} is given by $\mathit{acc} = N^{-1}\cdot\left|\mathcal{A}\right|$.
From the definition it is clear that $0\leq\mathit{acc} \leq 1$.

### 2021-01-22 paper2/1-introduction.tex
Some meager progress

As unlabelled data is much more freely available than labelled data, it is of interest to learn the representation in an unsupervised manner.
This will allow us to draw on a much more diverse pool of data to learn from.
% ; this is particularly pertinent for fair representation learning as unlabelled data affords us a much more diverse pool of data to learn from.
%To this end, \cite{locatello2019fairness} recently made the connection from disentangled representations to fair representations:
%a model for disentanglement trained without knowledge of the sensitive attribute $s$
%nevertheless appears to improve fairness measures with respect to $s$.
%However, as pointed out by \cite{locatello2019challenging},
%some supervision or inductive bias is needed in order to recognise a well-disentangled representation.
While annotations for $y$ are often hard to come by (and often noisy \cite{KehCheQua18}),
annotations for the sensitive attribute $s$ are usually less so, as $s$ can often be obtained from demographic information provided by census data.
We thus consider the setting where the representation is learned from data
that is only labelled with $s$ and not $y$.
This is in contrast to most other representation learning methods.
% We thus consider the setting where data labelled with $s$ (partially labelled data) is available for learning the fair representation.
% Furthermore, we assume the existence of a set with $s$ labels
% whose distribution matches the deployment setting
We call the set used to learn the representation the \emph{representative} set,
because its distribution is meant to match the distribution of the deployment setting
(and is thus representative).
% We call this set the \emph{representative} set and its distribution is meant to match the distribution of the deployment setting.

>>>>

As unlabelled data is much more freely available than labelled data, it is of interest to learn the representation in an unsupervised manner.
This will allow us to draw on a much more diverse pool of data to learn from.
% ; this is particularly pertinent for fair representation learning as unlabelled data affords us a much more diverse pool of data to learn from.
%To this end, \cite{locatello2019fairness} recently made the connection from disentangled representations to fair representations:
%a model for disentanglement trained without knowledge of the sensitive attribute $s$
%nevertheless appears to improve fairness measures with respect to $s$.
%However, as pointed out by \cite{locatello2019challenging},
%some supervision or inductive bias is needed in order to recognise a well-disentangled representation.
While annotations for $y$ are often hard to come by (and often noisy \cite{kehrenberg2020tuning}),
annotations for the sensitive attribute $s$ are usually less so, as $s$ can often be obtained from demographic information provided by census data.
We thus consider the setting where the representation is learned from data
that is only labelled with $s$ and not $y$.
This is in contrast to most other representation learning methods.
% We thus consider the setting where data labelled with $s$ (partially labelled data) is available for learning the fair representation.
% Furthermore, we assume the existence of a set with $s$ labels
% whose distribution matches the deployment setting
We call the set used to learn the representation the \emph{representative} set,
because its distribution is meant to match the distribution of the deployment setting
(and is thus representative).
% We call this set the \emph{representative} set and its distribution is meant to match the distribution of the deployment setting.

### 2021-01-22 paper2/3-method.tex
Some meager progress

\subsection{Conditional Flow}\label{cflow}
% \subsubsection{Invertible Neural Networks.}
\textbf{Invertible Neural Networks.}
Invertible neural networks are a class of neural network architecture characterised by a bijective mapping between their inputs and output \cite{Dinh2014}. The transformations are designed such that their inverses and Jacobians are efficiently computable.
These flow-based models permit \emph{exact} likelihood estimation \cite{normflows2015} through the warping of a base density with a series of invertible transformations and computing the resulting, highly multi-modal, but still normalised, density, using the change of variable theorem:
% Flow-GAN \cite{grover2018flowgan} combines the \emph{exact} log-likelihood estimation of the invertible network with the adversarial training of a GAN.
\begin{align}
\begin{split}
  \log p(x) &= \log p(z) + 
   \sum \log \left| \det\left( \frac{\diff h_i}{ h_{i-1}}\right) \right|, %\\
  \quad p(z) = \mathcal{N}(z; 0, \mathbb{I})
  \label{eq:changeofvariables}
\end{split}
\end{align}
where $h_i$ refers to the outputs of the layers of the network and $p(z)$ is the base density, specifically an Isotropic Gaussian in our case.
Training of the invertible neural network is then reduced to maximising $\log p(x)$ over the training set,
i.e.\ maximising the probability the network assigns to samples in the training set.

@@

% \subsubsection{The Benefits of Bijectivity.}
\textbf{The Benefits of Bijectivity.}
Using an invertible network to generate our encoding, $\bm{z}_u$, carries a number of advantages over other approaches.
Ordinarily, the main benefit of flow-based models is that they permit exact density estimation. 
However, since we are not interested in sampling from the model's distribution, in our case the likelihood term serves as a regulariser, as it does for  \cite{JacSmeOya18}. 
Critically, this forces the mean of each latent dimension to zero enabling null-sampling. 
The invertible property of the network guarantees the preservation of all information relevant to $y$ which is independent of $s$, regardless of how it is allocated in the output space.
Secondly, we conjecture that the encodings are more robust to out-of-distribution data.
Whereas an autoencoder could map a previously seen input and a previously unseen input to the same representation,
an invertible network sidesteps this due to the network's bijective property, ensuring all relevant information is stored somewhere. This opens up the possibility of transfer learning between datasets with a similar manifestation of $s$, as we demonstrate in the Appendix~\ref{sec:transfer-learning}.

@@

% \textbf{Tuning the Partition Sizes.}

% \subsubsection{The Pitfalls of Adversarial Training.}

>>>>

\subsection{Conditional Flow}\label{cflow}
\subsubsection{Invertible Neural Networks}
Invertible neural networks are a class of neural network architecture characterised by a bijective mapping between their inputs and output \cite{Dinh2014}. The transformations are designed such that their inverses and Jacobians are efficiently computable.
These flow-based models permit \emph{exact} likelihood estimation \cite{normflows2015} through the warping of a base density with a series of invertible transformations and computing the resulting, highly multi-modal, but still normalised, density, using the change of variable theorem:
% Flow-GAN \cite{grover2018flowgan} combines the \emph{exact} log-likelihood estimation of the invertible network with the adversarial training of a GAN.
\begin{align}
\begin{split}
  \log p(x) &= \log p(z) + 
   \sum \log \left| \det\left( \frac{\diff h_i}{ h_{i-1}}\right) \right|, %\\
  \quad p(z) = \mathcal{N}(z; 0, \mathbb{I})
  \label{eq:changeofvariables}
\end{split}
\end{align}
where $h_i$ refers to the outputs of the layers of the network and $p(z)$ is the base density, specifically an Isotropic Gaussian in our case.
Training of the invertible neural network is then reduced to maximising $\log p(x)$ over the training set,
i.e.\ maximising the probability the network assigns to samples in the training set.

@@

\subsubsection{The Benefits of Bijectivity}
Using an invertible network to generate our encoding, $\bm{z}_u$, carries a number of advantages over other approaches.
Ordinarily, the main benefit of flow-based models is that they permit exact density estimation. 
However, since we are not interested in sampling from the model's distribution, in our case the likelihood term serves as a regulariser, as it does for  \cite{JacSmeOya18}. 
Critically, this forces the mean of each latent dimension to zero enabling null-sampling. 
The invertible property of the network guarantees the preservation of all information relevant to $y$ which is independent of $s$, regardless of how it is allocated in the output space.
Secondly, we conjecture that the encodings are more robust to out-of-distribution data.
Whereas an autoencoder could map a previously seen input and a previously unseen input to the same representation,
an invertible network sidesteps this due to the network's bijective property, ensuring all relevant information is stored somewhere. This opens up the possibility of transfer learning between datasets with a similar manifestation of $s$, as we demonstrate in the Appendix~\ref{sec:transfer-learning}.

@@

% \subsubsection{Tuning the Partition Sizes}

% \subsubsection{The Pitfalls of Adversarial Training}
